---
title: "Assignment - R introduction"
output: html_document
---

### Exercise 1

Define a vector named `num_vec` containing the values `33, 41, 512, 32, 44`. Define also a vector of numeric weights named `weights_vec` containing the values `1, 1, 4, 3, 2`.
Compute the weighted average, that is
\[
\frac{\sum_{i=1}^n x_i \cdot w_i}{\sum_{i=1}^n w_i}
\]
where $x_i$ is the $i$-th element of `num_vec`, $w_i$ is the $i$-th element of `weights_vec` and $n$ is the length of `num_vec`.

```{r}
# Your solution here
num_vec <- c(33, 41, 512, 32, 44)
weights_vec <- c(1, 1, 4, 3, 2)
result <- sum(num_vec*weights_vec)/sum(weights_vec)

result
```

_Hint_: use vector operations instead of loops. When in doubt for which function to use to perform a task, consult the help page

### Exercise 2
Define a function, named `weighted_mean`, that accepts two arguments:

  - `numbers`: a vector of numbers
  - `weights`: a vector of weights

Call the function you just defined using some data. Use vectors of length `3`, of length `6`, and of length `8`.
Try to use both named arguments and positional arguments in your function calls.

```{r}
# Your solution here
weighted_mean <- function(numbers, weights){
   
  return(c(sum(numbers*weights)/weights))
}
weighted_mean(c(3,6,8),c(3,6,8))
```

When using positional arguments, what happens when you swap the position of the values you pass to the function? Why?
  

### Exercise 4

Consider the `mean` function, which computes the average of the input vector. Consider the following code snippet:
```{r}
nums <- c(1, 3, 5, 2, 5, NA, 5, 3, 3)
mean(nums)
```
What is the result? NA
Why do you get such result? 
Write your answer below: 
Because NA is not avilable and this mean there is nothing to compare with or get average from it and as a result the result if NA.



### Exercise 5
Given the code snippet we also used in the previous exercise:
```{r}

nums <- c(1, 3, 5, 2, 5, NA, 5, 3, 3)
mean(nums, na.rm=TRUE)

```
How can we obtain the result _ignoring_ the `NA`? I.e. how can we get the average of the vector _without_ the `NA`?
_Hint: read the documentation of the `mean` function._

### Exercise 6
Consider the following code:
```{r}
x <- c(1,2,3,4,NA,5,7,8,NA,10)
mean(is.na(x))
```
what does it compute? In other words, what does it do? 
it ignore the NA and then calculate the rest of the result by taking average of it.
Turn the code snippet above in a function, giving it an appropriate name:
```{r} 
# Write your solution here
avg <- function(val){
  return(mean(is.na(val)))
}
avg(c(1,2,3,4,NA,5,7,8,NA,10))
```

### Exercise 7
Write `both_na()` , a function that takes two vectors of the same length and returns the number of positions that have an NA in both vectors.
```{r}
# Your solution here
both_na <- function(v1, v2){
   which(is.na(v1), is.na(v2))
}
both_na(c(1,2,3,4,NA,5,7,8,NA,10), c(1,2,3,4,NA,5,7,8,NA,10))
```

### Exercise 8
Describe the difference between `is.finite(x)` and `!is.infinite(x)`. To answer this question, try some invocations either in the console or in a code block.

is.finite as the name suggest return the finite value of a collection or vecotr and !is.infinite(x) is the opposite of it, which returns non-finite values.






